Native advertising as a content marketing strategy

### 2024-09-11 analysis/paper/paper.Rmd
weiter

dta <- read.xlsx(here("analysis", "data", "raw_data", "dta.xlsx"), sheetIndex = 1) %>%
  select(REACH, INDUSTRIJA, CLICKBAIT, OPREMA, `IZVORI...IZJAVE`)
```
</details>

@@

<details>
<summary>Some descriptive statistics/click to see the code</summary>
```{r warning=FALSE, message=FALSE,error=FALSE, echo=FALSE, results='hide'}

@@

>>>>

dta <- read.xlsx(here("analysis", "data", "raw_data", "dta.xlsx"), sheetIndex = 1) %>%
  select(FROM,REACH, INDUSTRIJA, CLICKBAIT, OPREMA, `IZVORI...IZJAVE`)
```
</details>
<br>

@@

<details>
<summary>Some descriptive statistics</summary>
```{r warning=FALSE, message=FALSE,error=FALSE, echo=FALSE, results='hide'}

@@

```{r analysis2, echo=F, eval=FALSE, message=F , warning= FALSE, results='hide'}

## Shapiro-Wilk test for normality

# non filtered
shapiro.test(dta$REACH)

#filtered
shapiro.test(filtered_dta$REACH)

## Kruskal-Wallis test CLICKBAIT vs REACH

```
## Kruskal-Wallis test CLICKBAIT vs OPREMA

```{r}
kruskal.test(REACH ~ OPREMA, data = dta)
## Kruskal-Wallis test CLICKBAIT vs REACH
```
## Kruskal-Wallis test CLICKBAIT vs IZJAVA

```{r}
kruskal.test(REACH ~ IZVORI...IZJAVE , data = dta)
```

# Chi-sq INDUSTRIJA vs IZVOR
```{r}
chisq.test(dta$INDUSTRIJA, dta$IZVORI...IZJAVE)
```

# Chi-sq INDUSTRIJA vs CLICKBAIT

```{r}
chisq.test(dta$INDUSTRIJA, dta$CLICKBAIT)

</details>
<br>
